Toadflax Analysis

### 2024-03-08 toadflax_report.qmd
commit

loadings.ggplot +
  geom_text(data = loadings.plot,
            aes(PC1, PC2, label = compound)) +
  annotate("text", x = 0.2, y = -0.15, 
           label = "Myrcene, B-Pinene, \nLimonene, Thujene", 
           hjust = 0, vjust = 1, size = 4, color = "black") +
  annotate("rect", xmin = 0.5, ymin = 0.5, xmax = 0.9, ymax = 0.9)

,
           label = "Decanal, Nonanal, \nDodecanal, Undecanal")
,
           hjust = 1, vjust = 1, size = 4, color = "black") +
  geom_rect(aes(xmin = -0.3, ))
?annotate
loadings.ggplot + 
  geom_label_repel(data = loadings.plot,
                   aes(PC1, PC2, label = compound),
                   size = 4,
                   fill = "white",
                   color = "black",
                   alpha = 0.7,
                   label.padding = unit(0.25, "lines"),
                   label.r = unit(0.15, "lines"))

>>>>

loadings.ggplot +
  geom_text(data = loadings.plot,
            aes(PC1, PC2, label = compound))
```

<img src="toadflax_plots/loadings_with_boxes.png" alt="Toadflax PCA Loadings Plot with Box Labels" width="650"/>

```{r more loading plots, echo = F}
loadings.ggplot + 
  geom_label_repel(data = loadings.plot,
                   aes(PC1, PC2, label = compound),
                   size = 4,
                   fill = "white",
                   color = "black",
                   alpha = 0.7,
                   label.padding = unit(0.25, "lines"),
                   label.r = unit(0.15, "lines"))
